---
title: "Phase 2 solutions"
output:
  html_document:
    css: ~/GitHub/fear-of-childbirth/libs/css/sidebar.css
    highlight: tango
    keep_md: yes
    theme: flatly
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 12,
  fig.width = 11,
  # out.width = "550px",
  fig.path = 'figure_rmd_phase_3_5f/',     
  dev = "png",
  dpi = 100
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/extract-and-eliminate/extract-and-eliminate.R") 
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='hide', message=FALSE}
```

```{r function-correlation, echo=echoChunks, results='show', message=FALSE}
```
 

```{r function-rotation, echo=echoChunks, results='show', message=FALSE}
```
# Phase 2
After analysing the remaining 44 items retained in phase 1, we have decided to exclude itmes that showed small (less than ~.40) loadings across rotations. The following items has been eliminated during phase 2 of the analysis:  

- item 31

> Vaginal tearing during labour/birth?


- item 32

> Rectal tearing/damage as a consequence of labour/birth?


- item 46

> Needing to have stitches after the birth?



```{r data-phase-0, echo=echoChunks, results='hide', message=FALSE}
```

```{r data-phase-1, echo=echoChunks, results='hide', message=FALSE}
```

```{r data-phase-2, echo=echoChunks, results='hide', message=FALSE}
```


```{r  echo=echoChunks, results='asis', message=FALSE, warning=FALSE, eval=T}
phase <- "2"
R <- R2 # correlation matrix for items at phase 0
sample_size <- 643
k <- 4
# for(rotation_ in c("oblimin","geominQ")){   # },"quartimin","geominQ","bifactorQ")){
for(rotation_ in c("oblimin")){ 
  
  cat("\n\n")
  cat(paste0("## ",rotation_))
  for(nfactors_ in c(5)){
    # for(nfactors_ in c(4:10)){  
    mainTitle <- paste0(rotation_,", phase ",phase)
    cat("\n\n") 
    cat(paste0("### ",nfactors_));  
    cat("\n\n") 
    solution <- display_solution(R,k=nfactors_,sample_size,rotation_,mainTitle=mainTitle) %>% 
      print() 
    cat("\n\n")
    
    
  }  
}
```

