---
title: "Revision comments"
output:
  html_document:
    css: ~/GitHub/fear-of-childbirth/libs/css/sidebar.css
    highlight: tango
    keep_md: yes
    theme: flatly
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  # fig.height = 12,
  # fig.width = 11,
  out.width = "900px",
  fig.path = 'figure_rmd_phase_1/',     
  dev = "png",
  dpi = 100
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./reports/extract-and-eliminate/extract-and-eliminate.R") 
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```

<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='hide', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='hide', message=FALSE}
```

```{r function-correlation, echo=echoChunks, results='show', message=FALSE}
```

```{r function-rotation, echo=echoChunks, results='show', message=FALSE}
```

```{r data-phase-0, echo=echoChunks, results='hide', message=FALSE}
```

```{r data-phase-1, echo=echoChunks, results='hide', message=FALSE}
```

# Revision comments

## 3. Fit statistics.

> 3.	SPSS does not provide fit statistics for exploratory factor analysis. In order to convince me of the structure of your measure, you have to provide fit statistics. For example, M plus provides fit statistics for such analyses (also see reviewer 3; and M plus will provide geomin rotation), besides chi-squared, RMSEA (and confidence interval), also report at least CFI and TLI.

Response:

Here are the fit statistics for factor analytic solution in table and graphic format. 

```{r FA-statistics, echo=echoChunks, results='show', message=FALSE}
```

## 4. Number of factors

> Using the standard scree plot is an outdated approach to select the number of factors. So please follow his advice and apply a more advanced method such as parallel analysis or the MAP test or if you use a scree plot, do this on basis of fit statistics like for example the Hull method described by Lorenzo-Seva, Timmerman and Kiers (2011).

### PA with `psych`

Using `psych` package.
```{r PA-psych, echo=TRUE, results='show', message=FALSE, out.width = "900px"}
```

### PA with `nFactors`

Using `nFactors` package. 
```{r PA-nFactors, echo=TRUE, results='show', message=FALSE}
```

### PA with simulation engine
Compare observed eigenvalues with values simulated by 

> Patil, Vivek H., Surendra N. Singh, Sanjay Mishra,and D. Todd Donavan (2007), [Parallel Analysis Engine to Aid Determining Number of Factors to Retain](http://smishra.faculty.ku.edu/parallelengine.htm) [Computer software]. 

```{r compare-eigens, echo=echoChunks, results='show', message=FALSE}
```


### Velicer's MAP Test

```{r MAP-paramap, echo=echoChunks, results='show', message=FALSE}
```


